---
title: "Iteration and List Columns"
output: github_document
date: "2022-11-01"
---

```{r setup, include = FALSE}
library(tidyverse)
set.seed(1)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Lists

In R, vectors are limited to a single data class – all elements are characters, or all numeric, or all logical. Trying to join the following vectors will result in coersion, as would creating vectors of mixed types.

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

Lists contain indexed elements, and the indexed elements themselves be scalars, vectors, or other things entirely.

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

### Accessing list items

Lists can be accessed using names or indices, and the things in lists can be accessed in the way you would usually access an object of that type. DO NOT USE DOLLAR SIGNS IN YOUR CODE!

```{r}
l$vec_numeric

l[[1]]

l[[1]][1:3]

l[["mat"]]
```

## For loops

Let's write a for loop to take the mean and SD of four samples from a normal distribution.


```{r}
list_norms = 
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, .4),
    d = rnorm(20, 100, 1)
  )

is.list(list_norms)
```

Here's my function:

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

I can apply that function to each list element. Let's try to make this work:

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```
This is not very concise. Let's try a `for` loop instead!

We will create a vector of class "list" with a length of 4. We want to output the mean and sd of each element in `list_norms`, such that we want `output[[1]] = mean_and_sd(list_norms[[1]])` from 1 to 4.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

output
```

# Let's try map!

Map applies the `mean_and_sd` function onto `list_norms` --> same output as running the for loop.
It also applies names to each output.

```{r}
map(list_norms, mean_and_sd)
```

What if you want a different function...? We can "map" across `list_norms` any function!

```{r}
output = map(list_norms, median)
output

output = map(list_norms, IQR)
output
```

Map variants...
What if we don't want our output to be a "list"?

```{r}
output = map_dbl(list_norms, median)
output

```

More complicated...
We can't apply dbl to mean_and_sd because the function gives two numbers. However, we can output a dataframe!

```{r}
output = map_df(list_norms, mean_and_sd, .id = "input")
output

```

We keep track of the id under the "input" column.

## List columns!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"), 
    samp = list_norms
  )
```

When we print this, we get a weird output. Under "samp", we get have a named list, which is a collection of doubles of length 20.

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")
```

listcol_df has everything we have.

Let's try some operations.

```{r}
listcol_df$samp[[1]] # Gives us first element of 'samp' list column
mean_and_sd(listcol_df$samp[[2]])

```

Can I just...map? We will apply `mean_and_sd` to each element of the `samp` list column within the `listcol` dataframe.

```{r}
map(listcol_df$samp, mean_and_sd)
```

So...can I add a list column to our existing `listcol_df`? Use `mutate`!!

```{r}
listcol_df = listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd),
    medians = map_dbl(samp, median)
  )

```

This is fantastic! In this df, we have the name, sample list we started with, and the result stored as a list (of tibbles). We don't lose information.
