---
title: "Simulations"
output: github_document
date: "2022-11-03"
---

```{r setup, include = FALSE}
library(tidyverse)
set.seed(1)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Simulations!!

Here's our function from before.

```{r}
sim_mean_sd = function(n_obs, mu = 7, sigma = 4) {
  
  x = rnorm(n = n_obs, mean = mu, sd = sigma)

tibble(
  mu_hat = mean(x), 
  sigma_hat = sd(x)
)
}
```

How did we use this before?

```{r}
sim_mean_sd(n_obs = 30)
```
Every time we run this function, we get different estimates. Can we do this 100 times? 1000 times?

How can we use this now...a for loop perhaps?
We can create a vector with 100 empty spots, and fill these columns with `sim_mean_sd`.

```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(n_obs = 30)
  
}

bind_rows(output)
```


Let's use list columns instead! `expand_grid` gives us all possible combinations of sample size = 30 and iteration from 1 to 100. Then, we use `map` to input the results of `sim_mean_sd` into our df.

```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iteration = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)

sim_results_df
```

Let's plot some summaries for our simulation results.

```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) + 
  geom_density()
```

