---
title: "Writing Functions"
output: github_document
date: "2022-10-27"
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
set.seed(1)

```

## My first function

Let's compute the Z-score version of a list of numbers! 

```{r}
x_vec = rnorm(25, mean = 7, sd = 4)
(x_vec - mean(x_vec)) / sd(x_vec)
```

Suppose you want to do this often.

```{r}
z_scores = function(x) {
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  z #or return(z)
}
```
Now we have a `z_scores` function!

```{r}
z_scores(x_vec)

z_scores(x = 1:10)
z_scores(x = rbinom(100, 1, 0.6))
#z_scores(x = 3) #Can't take the sd() of 3, so returns NA
#z_scores(x = "My name is Cathy") #Can't take the sd() or mean() of characters
```


## Let's have multiple outputs

Let's just get the mean and sd from the vector input.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(mean = mean_x, 
       sd = sd_x)
}
```

```{r}
mean_and_sd(x_vec)
```

```{r}
mean_and_sd(x_vec)

mean_and_sd(x = 1:10)
mean_and_sd(x = rbinom(100, 1, 0.6))
#mean_and_sd(x = 3) 
#mean_and_sd(x = "My name is Cathy") 
```

## Simulations

When we compute the mean and sd each time, we are getting different values each time.


```{r}
x_vec = rnorm(n = 25000, mean = 7, sd = 4)

tibble(
  mean = mean(x_vec), 
  sd = sd(x_vec)
)
```

Can I do this using a function? YUP

```{r}
sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {
  
  x = rnorm(n = n_obs, mean = true_mean, sd = true_sd)

tibble(
  mean = mean(x), 
  sd = sd(x)
)
}
```

Does it work??

```{r}
sim_mean_sd(n_obs = 25)
```

We can see when running the function, we are getting a tibble that outputs the true mean and sd each time. When we don't set `true_mean` and `true_sd`, it defaults to the values we set of 7 and 4. If you don't name the arguments of the function, it will assume you are putting in order of the arguments of the function.