---
title: "Writing Functions"
output: github_document
date: "2022-10-27"
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
set.seed(1)

```

## My first function

Let's compute the Z-score version of a list of numbers! 

```{r}
x_vec = rnorm(25, mean = 7, sd = 4)
(x_vec - mean(x_vec)) / sd(x_vec)
```

Suppose you want to do this often.

```{r}
z_scores = function(x) {
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  z #or return(z)
}
```
Now we have a `z_scores` function!

```{r}
z_scores(x_vec)

z_scores(x = 1:10)
z_scores(x = rbinom(100, 1, 0.6))
#z_scores(x = 3) #Can't take the sd() of 3, so returns NA
#z_scores(x = "My name is Cathy") #Can't take the sd() or mean() of characters
```


## Let's have multiple outputs

Let's just get the mean and sd from the vector input.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(mean = mean_x, 
       sd = sd_x)
}
```

```{r}
mean_and_sd(x_vec)
```

```{r}
mean_and_sd(x_vec)

mean_and_sd(x = 1:10)
mean_and_sd(x = rbinom(100, 1, 0.6))
#mean_and_sd(x = 3) 
#mean_and_sd(x = "My name is Cathy") 
```

## Simulations

When we compute the mean and sd each time, we are getting different values each time.


```{r}
x_vec = rnorm(n = 25000, mean = 7, sd = 4)

tibble(
  mean = mean(x_vec), 
  sd = sd(x_vec)
)
```

Can I do this using a function? YUP

```{r}
sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {
  
  x = rnorm(n = n_obs, mean = true_mean, sd = true_sd)

tibble(
  mean = mean(x), 
  sd = sd(x)
)
}
```

Does it work??

```{r}
sim_mean_sd(n_obs = 25)
```

We can see when running the function, we are getting a tibble that outputs the true mean and sd each time. When we don't set `true_mean` and `true_sd`, it defaults to the values we set of 7 and 4. If you don't name the arguments of the function, it will assume you are putting in order of the arguments of the function.

## Fixing bad stuff

In reading data from the web, we wrote code that allowed us to scrape information in Amazon reviews. That code is below.


```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Let’s write a quick function to scrape review information for any URL to an Amazon review page.

```{r}
read_page_reviews = function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Let's try with a URL.

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=4"

read_page_reviews(url)
```

What good does this do? 
We’ll use this to read in reviews from a few pages and combine the results.



```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```

## Loading LoTR data

In tidy data, we broke the “only copy code twice” rule when we used the code below to process the LoTR words data:

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 

```

The function below will read in and clean LoTR data – it differs from the previous code by including some data tidying steps in the function rather than after data have been combined, but produces the same result.


```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```

## Functions as arguments

One powerful tool is the ability to pass functions as arguments into functions. This might seem like a weird thing to do, but it has a lot of handy applications – we’ll see just how far it goes in the next modules in this topic.

Do NOT use variable names you created in your function outside your function!

```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)
my_summary(x_vec, IQR)
my_summary(x_vec, var)

```

